Introducing ICBe: An Event Extraction Dataset from Narratives about International Crises

### 2023-11-21 replication_paper/psrm_draft/ICBe_manuscript.Rmd
small edit

First, re-programmable coding means scholars can make modifications to the ontology we provide and re-run the code script to produce a modified dataset. For example, if thoughts and speech acts are immaterial for a particular research question, those higher-level categories can be modified in a way that does not produce inevitable downstream effects on the rest of the coding. This is necessary because unlike existing datasets where variable values are largely independent, the nested nature of the ICBe variables means filtering out speech acts also requires filtered out variables about the actors, locations, and timing of those speech acts.

Second, no existing event data distinguishes thoughts, speeches, and actions. In fact, most only try to code actions and entirely omit thoughts and speech acts despite recognition of their importance in international politics [@smithInternationalCrisesDomestic1998]. Scholars have opted against coding thoughts and speech acts because of a lack of confidence the full universe could be readily observed and consequently at least theoretically be included.[^7] But the perfect should not be the enemy of the good, and measurement challenges are only overcome after an initial attempt to estimate difficult to observe concepts of interest. The ICB narratives are one of the better sources for this endeavor due to the consistent use of high-quality primary source material that takes advantage of qualitative methods well-suited to identifying thoughts and speech acts like archival work and expert interviews. Important questions about potential bias remain like whether a thought was known at the time by those involved or only recorded long afterwards by historians, but data validation required there to be data to be validated. By design, existing datasets largely omit thoughts and speech acts and also treat the resulting dataset as the static product of hardwired coding decisions. In allowing scholars to identify actions, thoughts, and speech acts as distinct characteristics of international crises while also granting flexibility about the inclusion of a non-random sample of novel variables, our approach is a notable improvement over the state of the art.

>>>>

First, re-programmable coding means scholars can make modifications to the ontology we provide and re-run the code script to produce a modified dataset. For example, if thoughts and speech acts are immaterial for a particular research question, those higher-level categories can be modified in a way that does not produce inevitable downstream effects on the rest of the coding. This is necessary because unlike existing datasets where variable values are largely independent, the nested nature of the ICBe variables means filtering out speech acts also requires filtering out variables about the actors, locations, and timing of those speech acts.

Second, no existing event data distinguishes thoughts, speeches, and actions. In fact, most only try to code actions and entirely omit thoughts and speech acts despite recognition of their importance in international politics [@smithInternationalCrisesDomestic1998]. Scholars have opted against coding thoughts and speech acts because of a lack of confidence the full universe could be readily observed and consequently at least theoretically be included.[^7] But the perfect should not be the enemy of the good, and measurement challenges are only overcome after an initial attempt to estimate difficult-to-observe concepts of interest. The ICB narratives are one of the better sources for this endeavor due to the consistent use of high-quality primary source material that takes advantage of qualitative methods well-suited to identifying thoughts and speech acts like archival work and expert interviews. Important questions about potential bias remain like whether a thought was known at the time by those involved or only recorded long afterwards by historians, but data validation required there to be data to be validated. By design, existing datasets largely omit thoughts and speech acts and also treat the resulting dataset as the static product of hardwired coding decisions. In allowing scholars to identify actions, thoughts, and speech acts as distinct characteristics of international crises while also granting flexibility about the inclusion of a non-random sample of novel variables, our approach is a notable improvement over the state of the art.

### 2023-11-21 replication_paper/psrm_draft/ICBe_manuscript.tex
small edit

\hhline{>{\arrayrulecolor[HTML]{000000}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}

@@

First, re-programmable coding means scholars can make modifications to
the ontology we provide and re-run the code script to produce a modified
dataset. For example, if thoughts and speech acts are immaterial for a
particular research question, those higher-level categories can be
modified in a way that does not produce inevitable downstream effects on
the rest of the coding. This is necessary because unlike existing
datasets where variable values are largely independent, the nested
nature of the ICBe variables means filtering out speech acts also
requires filtered out variables about the actors, locations, and timing
of those speech acts.

Second, no existing event data distinguishes thoughts, speeches, and
actions. In fact, most only try to code actions and entirely omit
thoughts and speech acts despite recognition of their importance in
international politics (Smith 1998). Scholars have opted against coding
thoughts and speech acts because of a lack of confidence the full
universe could be readily observed and consequently at least
theoretically be included.\footnote{Even the coding of overt actions
  like MIDs is not without contention (Gibler 2018).} But the perfect
should not be the enemy of the good, and measurement challenges are only
overcome after an initial attempt to estimate difficult to observe
concepts of interest. The ICB narratives are one of the better sources
for this endeavor due to the consistent use of high-quality primary
source material that takes advantage of qualitative methods well-suited
to identifying thoughts and speech acts like archival work and expert
interviews. Important questions about potential bias remain like whether
a thought was known at the time by those involved or only recorded long
afterwards by historians, but data validation required there to be data
to be validated. By design, existing datasets largely omit thoughts and
speech acts and also treat the resulting dataset as the static product
of hardwired coding decisions. In allowing scholars to identify actions,
thoughts, and speech acts as distinct characteristics of international
crises while also granting flexibility about the inclusion of a
non-random sample of novel variables, our approach is a notable
improvement over the state of the art.

>>>>

\hhline{>{\arrayrulecolor[HTML]{FFFFFF}\global\arrayrulewidth=0pt}-~~|~~~~~~~|~~~}

@@

First, re-programmable coding means scholars can make modifications to
the ontology we provide and re-run the code script to produce a modified
dataset. For example, if thoughts and speech acts are immaterial for a
particular research question, those higher-level categories can be
modified in a way that does not produce inevitable downstream effects on
the rest of the coding. This is necessary because unlike existing
datasets where variable values are largely independent, the nested
nature of the ICBe variables means filtering out speech acts also
requires filtering out variables about the actors, locations, and timing
of those speech acts.

Second, no existing event data distinguishes thoughts, speeches, and
actions. In fact, most only try to code actions and entirely omit
thoughts and speech acts despite recognition of their importance in
international politics (Smith 1998). Scholars have opted against coding
thoughts and speech acts because of a lack of confidence the full
universe could be readily observed and consequently at least
theoretically be included.\footnote{Even the coding of overt actions
  like MIDs is not without contention (Gibler 2018).} But the perfect
should not be the enemy of the good, and measurement challenges are only
overcome after an initial attempt to estimate difficult-to-observe
concepts of interest. The ICB narratives are one of the better sources
for this endeavor due to the consistent use of high-quality primary
source material that takes advantage of qualitative methods well-suited
to identifying thoughts and speech acts like archival work and expert
interviews. Important questions about potential bias remain like whether
a thought was known at the time by those involved or only recorded long
afterwards by historians, but data validation required there to be data
to be validated. By design, existing datasets largely omit thoughts and
speech acts and also treat the resulting dataset as the static product
of hardwired coding decisions. In allowing scholars to identify actions,
thoughts, and speech acts as distinct characteristics of international
crises while also granting flexibility about the inclusion of a
non-random sample of novel variables, our approach is a notable
improvement over the state of the art.
